A comparison of classification algorithms applied to the Adult Database

### 2009-12-09 report/final.tex
experimenta evaluation of CART.

\begin{table}[ht]
  \begin{center}
  \begin{tabular}{ | l | c | c | c | c | c |}
    \hline
    \textbf{Parameters} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} & \textbf{Nodes} & \textbf{Leaves} \\ \hline
    -M 2 -N 5 & 13.96 & 25.37 & 3m6.315s & 119 & 60 \\ \hline
    -M 2 -N 10 & 13.85 & 25.38 & 5m36.925s & 139 & 70 \\ \hline
    -M 2 -N 15 & 13.93 & 25.41 & 8m1.214s & 123 & 62 \\ \hline

  \end{tabular}
  \caption{Results for CART.}
  \label{tbl:results_cart}
  \end{center}
\end{table}

CART results are displayed in Table \ref{tbl:results_cart}.

>>>>

\begin{table}[ht]
  \begin{center}
  \begin{tabular}{ | l | c | c | c | c | c |}
    \hline
    \textbf{Parameters} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} & \textbf{Nodes} & \textbf{Leaves} \\ \hline
    -M 2 -N 5 & 13.96 & 25.37 & 3m6.315s & 119 & 60 \\ \hline
    -M 2 -N 10 & 13.85 & 25.38 & 5m36.925s & 139 & 70 \\ \hline
    -M 2 -N 15 & 13.93 & 25.41 & 8m1.214s & 123 & 62 \\ \hline
    -M 2 -N 20 & 13.88 & 25.39 & 10m27.982s & 133 & 67 \\ \hline

    -M 3 -N 5 & 13.96 & 25.37 & 2m51.491s & 119 & 60 \\ \hline
    -M 3 -N 10 & 13.85 & 25.39 & 5m18.642s & 139 & 70 \\ \hline
    -M 3 -N 15 & 13.94 & 25.41 & 7m53.984s & 123 & 62 \\ \hline
    -M 3 -N 20 & 13.88 & 25.39 & 10m19.665s & 133 & 67 \\ \hline

    -M 5 -N 5 & 13.94 & 25.41 & 2m43.363s & 123 & 62 \\ \hline
    -M 5 -N 10 & 13.82 & 25.34 & 4m54.547s & 145 & 73 \\ \hline
    -M 5 -N 15 & 13.94 & 25.41 & 7m9.537s & 123 & 62 \\ \hline
    -M 5 -N 20 & 13.88 & 25.39 & 9m18.095s & 133 & 67 \\ \hline
  \end{tabular}
  \caption{Results for CART.}
  \label{tbl:results_cart}
  \end{center}
\end{table}

CART results are displayed in Table \ref{tbl:results_cart}.
From these results we can see that there isn't a lot of variation in the results.
The algorithm also performs badly when compared to C4.5 or ADTree.
